More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-10-17 2016-Weak-FH-Bisim/WeakBisim.tex
Small changes during the meeting

The equivalence we need is a strong bisimulation between
pNets having exactly the same Holes with the same sorts, but using a
flexible matching 
between open transition, to accommodate comparisons between pNet
expressions with different architectures.
 We name it FH-bisimulation,
 as a short cut for the ``Formal Hypotheses'' manipulated in the
 transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
 that pioneered this idea.\\
\TODO{To check:}
Let \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s^1,s^2)$, there is a 
   single
      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related 
      if $\Pred_{s^1,s^2}$ 
      is 
      true, i.e. the states are related when the variables in $s^1$ and $s^2$ verify the 
      predicate $\Pred_{s^1,s^2}$.

\RAB{ I propose:
Let $\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$ be a relation over the set 
$\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate: if $(s^1,s^2) \in 
\mathcal{R}$ then $\Pred_{s^1,s^2}$ is  true.}  \LUDO{No : this is not the meaning}

@@

       	It is trivial to check reflexivity and symmetry. Here we focus on the
       	transitivity. 
       	To prove transitivity of strong FH-bisimulation on pNets it is sufficient to 
       	prove 
       	transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ 
       	in those 
       	automata\footnote{We omit the constraints stating that each $s^i_x$ is in the 
       	states of 
       		$\mathcal{T}_i$ for the sake of readability}.
       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
       	$(s^1,s^2|\Pred)$.
       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
       	of 
       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}2$ are of the 
       	form 
       	$(s^2,s^3|\Pred\,')$.

@@

This relation is the adaptation of the transitivity to the conditional relationship that 
defines a bisimulation. Indeed the global disjunction together with the conjunction of 
predicates plays exactly the role of the intermediate element in a transitivity rule: 
``there exists an intermediate state'' corresponds to the global disjunction, and the 
conjunction of states expresses the intermediate predicate is used to ensure 
satisfiability of the predicate relating the first state to the last one..

@@

       	For any $p\in P$ by definition of $\mathcal{R}''$,
       	$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. 
       	We have 
       	the 
       	following by definition of bisimulation.
       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
       	Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
       	\begin{mathpar}

@@

       	there exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:

@@

       	for any open transition $OT_{px}$, since
       	$(s^2_p,s^3|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
       	$OT_{pxy}^{x\in X, y\in Y} \subseteq \mathcal{T}_3$:

@@

       	\end{mathpar}
       	such that  $\forall y, J_{2px}=J_{3pxy}, 
       	(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_p \land \Pred_{OT_x}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land v_{px}\!=\!v_{pxy} \land
       	\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.

>>>>

The equivalence we need is a strong bisimulation between
pNets having exactly the same Holes with the same sorts, but using a
flexible matching 
between open transition, to accommodate comparisons between pNet
expressions with different architectures.
 We name it FH-bisimulation,
 as a short cut for the ``Formal Hypotheses'' manipulated in the
 transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
 that pioneered this idea.

Let \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s^1,s^2)$, there is a 
   single
      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related 
      if $\Pred_{s^1,s^2}$ 
      is 
      true, i.e. the states are related when the variables in $s^1$ and $s^2$ verify the 
      predicate $\Pred_{s^1,s^2}$.

@@

       	It is trivial to check reflexivity and symmetry. Here we focus on the
       	transitivity. 
       	To prove transitivity of strong FH-bisimulation on pNets it is sufficient to 
       	prove 
       	transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ 
       	in those 
       	automata\footnote{We omit the constraints stating that each $s^i_x$ is in the 
       	states of 
       		$\mathcal{T}_i$ for the sake of readability}.
       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
       	$(s^1,s^2|\Pred)$.
       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
       	of 
       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
       	form 
       	$(s^2,s^3|\Pred\,')$.

@@

This relation is the adaptation of the transitivity to the conditional relationship that 
defines a bisimulation. Indeed the global disjunction together with the conjunction of 
predicates plays exactly the role of the intermediate element in a transitivity rule: 
``there exists an intermediate state'' corresponds to the global disjunction, and the 
conjunction of states expresses the intermediate predicate is used to ensure 
satisfiability of the predicate relating the first state to the last one.

@@

       	For any $p\in P$ by definition of $\mathcal{R}''$,
       	$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and 
       	$(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}'$. 
       	We have 
       	the 
       	following by definition of bisimulation.
       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$.
       	Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
       	\begin{mathpar}

@@

       	There exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:

@@

       	for any open transition $OT_{px}$, since
       	$(s^2_p,s^3|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
       	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:

@@

       	\end{mathpar}
       	such that  $\forall y, J_{2px}=J_{3pxy}, 
       	(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_p \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land v_{px}\!=\!v_{pxy} \land
       	\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.
